%کلمات کلیدی انگلیسی
\latinkeywords{Usability, Quality Models, Crowdsourcing, Web Applications}
%چکیده انگلیسی

\en-abstract{
Reviewing the quality models presented from 1970 to now, it is determined, with a high approximately, that every quality model acknowledges the usability as a main factor of quality of software. What is common in multiple definitions of the term "usability", is that there is always three items included: the user, doing a specific task, an interface which the user interacts with to do the task. As a software engineer, increasing the quality and the decreasing the cost of the defects or change requests is a great challenge which requires a lot of effort. Web applications, being a software product that aesthetics, interface, and the communication protocol of them are crucial, have a very widespread usage these days. Hence they can play a major role in multiple aspects of our lives, including the success of industrial projects, startups or improving everyday life. It is proven that one of the main cons of web application, is their not-so-much user-friendly design, which leads to major costs in businesses. Although, ideally all the administrative decisions, including selecting the proper software process, are being made based on the valuable experiences and cautiously, it is seen in most of the cases, like Google's calendar, a not-usable user interface, would lead to major costs to the whole software engineering team. Hence, with a look into a few resources, doing a pre-test (before the release) in all the aspects, including the UI design itself, is crucial for the success of every software product. But mockups and sketches, due to their artistic nature, are very hard to evaluate and the answer to a question like "Which UI is a good one?" will be a very hard one. Besides, the technology is changing quickly and as time goes on, we will see major changes in the requirements. So checklists and guidelines which are introduced in some references are not a good answer to these types of questions. Conducting a comparative study on quality models being proposed from 1970, it is easy to say that they are multiple metrics introduced for usability in every quality model; One of the very recent models was proposed in 2013 which we took it as a basis for this project due to it's focus on usability. Reviewing the available tools for measuring the usability of software products, we can see that none of these tools consider the metrics introduced in this model as a whole and instead they use only a partial model. So we have implemented a usability testing tool which considers all the metrics introduced in 2013 and gives the user the ability to perform the tests using crowdsourcing platforms.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}
\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}